---
output:
  pdf_document: default
  html_document: default
---

#Packages
```{r}
library(tidyverse)
library(tibble)
library(ggplot2)
```

# basic Import
#to import a file just simply use this template:
#Import = read.csv('Pathname')
#Import

```{r}
advertiser <- read_csv('/Users/nikodem/Desktop/dataset/advertiser.csv',col_names = TRUE)
advertiser

campaigns <- read_csv('/Users/nikodem/Desktop/dataset/campaigns.csv',col_names = TRUE)
campaigns

clicks <- read_csv('/Users/nikodem/Desktop/dataset/clicks.csv',col_names = TRUE)
clicks

conversions <- read_csv('/Users/nikodem/Desktop/dataset/conversions.csv',col_names = TRUE)
conversions

impressions <- read_csv('/Users/nikodem/Desktop/dataset/impressions.csv',col_names = TRUE)
impressions
```

#Count Function
this function just counts the number of observations found within the csv's this is done before joining as more information can be gathered and transferred over

```{r}
count_clicks <- clicks %>% count("campaign_id")
colnames(count_clicks) <- c("campaign_id","clicks")
view(count_clicks)

count_conversions <- conversions %>% count("campaign_id")
colnames(count_conversions) <- c("campaign_id","conversion")
view(count_conversions)

count_impressions <- impressions %>% count("campaign_id")
colnames(count_impressions) <-c("campaign_id","impressions")
view(count_impressions)

```

#join
let's join our brand new count tables mader above into a singular table called join
```{r}

join <- inner_join(advertiser,campaigns, by = c("ID" = "advertiser_id"))
colnames(join) <- c("advertiser_id","company","campaign_id","campaign","budget")

count_clicks$campaign_id <- as.character(count_clicks$campaign_id)
count_conversions$campaign_id <- as.character(count_conversions$campaign_id)
count_impressions$campaign_id <- as.character(count_impressions$campaign_id)
  
join$campaign_id <- as.character(join$campaign_id)

str(join)

join <- left_join(join, count_impressions, by =c("campaign_id"))
join <- left_join(join, count_clicks, by =c("campaign_id"))
join <- left_join(join, count_conversions, by =c("campaign_id"))

view(join)
```
i failed to get campaign_id as character somehow so i needed to force convert it to a character from a double i don't know why that happened but it messed up my whole assignment.
#join test/practice & info
#x <- tribble( ~key, ~val_x,1,"x1",2,"x2",3,"x3")
#y <- tribble( ~key, ~val_y,1,"y1",2,"y2",4,"y3")

#res <- inner_join(x, y, by = "key")

#resLeft <- left_join(x, y, by = "key")

#resRight <- right_join(x, y, by = "key")

#resFull <- full_join(x, y, by = "key")

#resSemi <- semi_join(x, y, by = "key")

#resAnti <- anti_join(x, y, by = "key")

the next step in my journey is looking if there is any missing data and if so substituting that missing data
```{r}
is.na(advertiser)
is.na(clicks)
is.na(conversions)
is.na(campaigns)
is.na(impressions)
```
since i am receiving error's as n/a lets change those to 0 from n/a to still make my data work when plotting
```{r}
join$impressions[which(is.na(join$impressions))]<- 0
join$clicks[which(is.na(join$clicks))]<- 0
join$conversion[which(is.na(join$conversion))]<- 0
view(join)
```
The final stage of this project is analysis
the analysis i will be performing is companies and campaigns to their budget
```{r}
ggplot(data=join, aes(x=campaign, y=budget)) +
  geom_bar(stat="identity", width=0.75, fill = 'blue') + ggtitle("Budget per Campaign")

ggplot(data=join, aes(x=company, y=budget)) +
  geom_bar(stat="identity", width=0.75, fill = 'purple') + ggtitle("Budget per company for campaigns")
```
finally i wanted to graphs clicks,impressions and conversions and compare to one another sadly my join didn't do correctly what i wanted and 
```{r}

ggplot(data=join, aes(x=count_clicks$clicks, y=count_impressions$impressions)) +
  geom_bar(stat="identity", width=0.5, fill = "darkblue") + ggtitle("Impressions per Campaign")



```

sadly i couldn't compare the two due to my time spent studying for exams, i know excuses are excuses but apologies for the rushed assignment.
